An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-15 EconGrowth-R-Functions.Rnw
Cleaning up the gamma grid graph.

###############################
# Does a grid search over values of gamma for a CD with energy production function.
# Results are returned as a data.frame with columns of gamma, SSE, lambda, alpha, and beta
##
cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
  lambda <- unlist(lapply(models, function(model){coef(model)["lambda"]}))
  alpha <- unlist(lapply(models, function(model){coef(model)["alpha"]}))
  data <- as.data.frame(cbind(gammaGrid, lambda, alpha, SSE))
  row.names(data) <- NULL #eliminates row names, leaving only numbered rows
  colnames(data) <- c("gamma", "lambda", "alpha", "SSE")
  data <- transform(data, beta = 1.0 - alpha - gamma)
  return(data)
}

@@

>>>>

###############################
# Does a grid search over values of gamma for a CD with energy production function.
# Results are returned as a data.frame with columns of gamma, SSE, lambda, alpha, and beta
##
cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
  lambda <- unlist(lapply(models, function(model){coef(model)["lambda"]}))
  alpha <- unlist(lapply(models, function(model){coef(model)["alpha"]}))
  data <- as.data.frame(cbind(gammaGrid, lambda, alpha, SSE))
  row.names(data) <- NULL #eliminates row names, leaving only numbered rows
  colnames(data) <- c("gamma", "lambda", "alpha", "SSE")
  data <- transform(data, beta = 1.0 - alpha - gamma)
  # Now make a column that has the country abbreviation
  nRowsData <- nrow(data) #Gets number of rows in data set
  dfOfCountryAbbrevs <- as.data.frame(matrix(countryAbbrev, ncol=1, nrow=nRowsData))
  colnames(dfOfCountryAbbrevs) <- "Country"
  data <- cbind(data, dfOfCountryAbbrevs) 
  return(data)
}

@@

# Creates a single graph or a multi-panel lattice plot showing grid search over gamma for Cobb-Douglas models with 
# the given quantification for energy.
# countryAbbrev: one of "US", "UK", "JP", "CN", "ZA", "SA", "IR", "TZ", or "ZM". Set to NA if you want a lattice
# plot for all countries
# energyType: one of "Q", "X", or "U"
cdeGridLattice <- function(energyType, countryAbbrev=NA, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc, textScaling = 1.0){
  gammaGrid <- seq(0.0, 0.95, by=0.05) # Establishes the grid in which we're interested.
  if (is.na(countryAbbrev)){
    # All countries are wanted.
    data <- do.call("rbind", lapply(countryAbbrevsAlph, cdeGridData, energyType=energyType, gammaGrid=gammaGrid))
    # Only one specific country is wanted.
    data <- cdeGridData(countryAbbrev=countryAbbrev, energyType=energyType, gammaGrid=gammaGrid)
  alphaBetaGammaRange <- c(0.0, 1.0)
  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
  lambdaRange <- c(0.0, 0.004)
  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
  sseRange <- c(0.0, 0.1)
  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08, 0.10)
  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
  graphType <- "b" #b is for both symbls and lines. Necessary so that the key looks right.
  lineTypes <- c(2, 1, 3, 0) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
  symbols <- c(NA, NA, NA, 1)
  colors <- c("black", "black", "black", "black") #line and symbol colors
  abgGraph <- xyplot(alpha+beta+gamma ~ gamma | Country, data=data,
                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
                     ylim=c(0.0, 1.5), #y axis limits
                     xlab=list(label="$\\gamma$", cex=textScaling), 
                     ylab=list(label="$\\alpha$, $\\beta$, $\\gamma$", cex=textScaling)
  sseGraph <- xyplot(SSE ~ gamma | Country, data=data,
                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
                                 y=list(at=sseTics) #location for y tics                                          
                     ylim=sseRange,
                     xlab=list(label="$\\gamma$", cex=textScaling), #Not used by the double-Y graph.
                     ylab=list(label="$SSE$", cex=textScaling)
  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)
  return(doubleYGraph)

### 2013-04-15 EconGrowth.Rnw
Cleaning up the gamma grid graph.

\item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.

@@

<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H">>=
cdeGridGraph(countryAbbrev="ZA", energyType="Q")
@

>>>>

\item{Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel. But, wait until we know if we have symmetric confidence intervals before doing this. These graphs won't work if we have asymmetric CIs.}

@@

<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
cdeGridGraph(countryAbbrev="ZA", energyType="Q")
@

<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H", eval=TRUE>>=
cdeGridLattice(energyType="Q")
@
